Strings functions analysis

### 2022-08-28 article.tex
all rust functions added

    \textbf{Rust}:

>>>>

    \textbf{Rust}: new, with\_capacity, from\_utf8, from\_utf8\_lossy, from\_utf16, from\_utf16\_lossy, from\_raw\_parts, from\_utf8\_unchecked, into\_bytes, as\_str, as\_mut\_str, push\_str, capacity, reserve, reserve\_exact, try\_reserve, try\_reserve\_exact, shrink\_to\_fit, shrink\_to, push, as\_bytes, truncate, pop, remove, retain, insert, insert\_str, as\_mut\_vec, len, is\_empty, split\_off, clear, drain, splice, into\_boxed\_str.
